---
title: "PERIPrem Truth Tables"
author: "Richard Blackwell"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(flextable)
library(officer)

source('periprem_reporting_functions.R')
```

### Gestation field

```{r tt_gestation, echo = FALSE}
df_tt <- data.frame(gestation = c('<26+6', '27 - 27+6', '28 - 29+6', '30 - 31+6', '32 - 33+6', NA)) %>%
  mutate(valid = fnCheck_gestation(.))

std_border <- fp_border(color = "gray")

ft <- flextable(df_tt) %>%
  set_header_labels(
    gestation = 'Gestation Length',
    valid = 'Logic Validity') %>%
  set_table_properties(layout = "autofit", width = .5) %>%
  hline(part = "body", border = std_border) %>%
#  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header") %>% 
  bg(j = 2, bg = function(x){ifelse(x, 'forestgreen', 'red4')}) %>%
  color(j = 2, color = 'white')
ft
```
### Weight field

```{r tt_weight, echo = FALSE}
df_tt <- data.frame(weight = c('<800g', '<1500g', '>1500g', NA)) %>%
  mutate(valid = fnCheck_weight(.))

std_border <- fp_border(color = "gray")

ft <- flextable(df_tt) %>%
  set_header_labels(
    weight = 'Birth Weight',
    valid = 'Logic Validity') %>%
  set_table_properties(layout = "autofit", width = .5) %>%
  hline(part = "body", border = std_border) %>%
#  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header") %>% 
  bg(j = 2, bg = function(x){ifelse(x, 'forestgreen', 'red4')}) %>%
  color(j = 2, color = 'white')
ft
```

### Number of births field

```{r tt_births, echo = FALSE}
df_tt <- data.frame(births = c('Single', 'Multiple', NA)) %>%
  mutate(valid = fnCheck_births(.))

std_border <- fp_border(color = "gray")

ft <- flextable(df_tt) %>%
  set_header_labels(
    births = 'Number of Births',
    valid = 'Logic Validity') %>%
  set_table_properties(layout = "autofit", width = .5) %>%
  hline(part = "body", border = std_border) %>%
#  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header") %>% 
  bg(j = 2, bg = function(x){ifelse(x, 'forestgreen', 'red4')}) %>%
  color(j = 2, color = 'white')
ft
```
### Ventilation field

```{r tt_ventilation, echo = FALSE}
df_tt <- data.frame(ventilation = c('No', 'Yes', NA)) %>%
  mutate(valid = fnCheck_ventilation(.))

std_border <- fp_border(color = "gray")

ft <- flextable(df_tt) %>%
  set_header_labels(
    ventilation = 'Invasive Ventilation',
    valid = 'Logic Validity') %>%
  set_table_properties(layout = "autofit", width = .5) %>%
  hline(part = "body", border = std_border) %>%
#  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header") %>% 
  bg(j = 2, bg = function(x){ifelse(x, 'forestgreen', 'red4')}) %>%
  color(j = 2, color = 'white')
ft
```

### Active labour field

```{r tt_labour, echo = FALSE}
df_tt <- data.frame(labour = c('No', NA, 'Yes')) %>%
  mutate(valid = fnCheck_labour(.))

std_border <- fp_border(color = "gray")

ft <- flextable(df_tt) %>%
  set_header_labels(
    labour = 'Active Labour',
    valid = 'Logic Validity') %>%
  set_table_properties(layout = "autofit", width = .5) %>%
  hline(part = "body", border = std_border) %>%
#  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header") %>% 
  bg(j = 2, bg = function(x){ifelse(x, 'forestgreen', 'red4')}) %>%
  color(j = 2, color = 'white')
ft
```

### Place of birth field

```{r tt_place, echo = FALSE}
df_tt <- data.frame(
  expand.grid(
    gestation = c('<26+6', '27 - 27+6', '28 - 29+6', '30 - 31+6', '32 - 33+6', NA),
    weight = c('<800g', '<1500g', '>1500g', NA),
    births = c('Single', 'Multiple', NA),
    place = c('No', NA, 'Yes')
  )) %>%
  mutate(valid = fnCheck_place(.)) %>%
  arrange(gestation, weight, births, place)

std_border <- fp_border(color = "gray")

ft <- flextable(df_tt) %>%
  set_header_labels(
    gestation = 'Gestation Length',
    weight = 'Birth Weight',
    births = 'Number of Births',
    place = 'Place of Birth',
    valid = 'Logic Validity') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header") %>% 
  bg(j = 5, bg = function(x){ifelse(x, 'forestgreen', 'red4')}) %>%
  color(j = 5, color = 'white')
ft
```

### Place of birth field (exc. NA for gestation, weight and number of births)

```{r tt_place_exc_na, echo = FALSE}
df_tt <- data.frame(
  expand.grid(
    gestation = c('<26+6', '27 - 27+6', '28 - 29+6', '30 - 31+6', '32 - 33+6', NA),
    weight = c('<800g', '<1500g', '>1500g', NA),
    births = c('Single', 'Multiple', NA),
    place = c('No', NA, 'Yes')
  )) %>%
  mutate(valid = fnCheck_place(.)) %>%
  arrange(gestation, weight, births, place)

std_border <- fp_border(color = "gray")

ft <- flextable(df_tt %>% 
                  filter(!is.na(gestation) &
                           !is.na(weight) &
                           !is.na(births))) %>%
  set_header_labels(
    gestation = 'Gestation Length',
    weight = 'Birth Weight',
    births = 'Number of Births',
    place = 'Place of Birth',
    valid = 'Logic Validity') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header") %>% 
  bg(j = 5, bg = function(x){ifelse(x, 'forestgreen', 'red4')}) %>%
  color(j = 5, color = 'white')
ft
```

## Antenatal steroids section

### Antenatal steroids given field

```{r tt_steroids_rx, echo = FALSE}
df_tt <- data.frame(steroids_rx = c('No', 'Yes', NA)) %>%
  mutate(valid = fnCheck_steroids_rx(.))

std_border <- fp_border(color = "gray")

ft <- flextable(df_tt) %>%
  set_header_labels(
    steroids_rx = 'Antenatal steroids given',
    valid = 'Logic Validity') %>%
  set_table_properties(layout = "autofit", width = .5) %>%
  hline(part = "body", border = std_border) %>%
#  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header") %>% 
  bg(j = 2, bg = function(x){ifelse(x, 'forestgreen', 'red4')}) %>%
  color(j = 2, color = 'white')
ft
```

### Antenatal steroids doses field

```{r tt_steroids_doses, echo = FALSE}
df_tt <- data.frame(
  expand.grid(
    steroids_rx = c('No', 'Yes', NA),
    steroids_doses = c('0', '1', '2', NA)
  )) %>%
  mutate(valid = fnCheck_steroids_doses(.)) %>%
  arrange(steroids_rx, steroids_doses)

std_border <- fp_border(color = "gray")

ft <- flextable(df_tt) %>%
  set_header_labels(
    steroids_rx = 'Antenatal steroids given',
    steroids_doses = 'Number of doses',
    valid = 'Logic Validity') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header") %>% 
  bg(j = 3, bg = function(x){ifelse(x, 'forestgreen', 'red4')}) %>%
  color(j = 3, color = 'white')
ft
```

### Antenatal steroids administration optimisation possible

```{r tt_steroids_opt_poss, echo = FALSE}
df_tt <- data.frame(
  expand.grid(
    steroids_rx = c('No', 'Yes', NA),
    steroids_opt_poss = c('No', 'Yes', NA)
  )) %>%
  mutate(valid = fnCheck_steroids_opt_poss(.)) %>%
  arrange(steroids_rx, steroids_opt_poss)

std_border <- fp_border(color = "gray")

ft <- flextable(df_tt) %>%
  set_header_labels(
    steroids_rx = 'Antenatal steroids given',
    steroids_opt_poss = 'Optimal Adminstration Possible',
    valid = 'Logic Validity') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header") %>% 
  bg(j = 3, bg = function(x){ifelse(x, 'forestgreen', 'red4')}) %>%
  color(j = 3, color = 'white')
ft
```

### Antenatal steroids administration optimisation achieved

The structure of this check is poorly coded on my part at the moment, but aside
from that the current validity check does not take into account the doses, so an
entry that has a mother in receipt of antibiotics but only one doses can still be
counted as optimal.

```{r tt_steroids_opt_act, echo = FALSE}
df_tt <- data.frame(
  expand.grid(
    steroids_rx = c('No', 'Yes', NA),
    steroids_opt_poss = c('No', 'Yes', NA),
    steroids_opt_act = c('No', 'Yes', NA)
  )) %>%
  mutate(valid = fnCheck_steroids_opt_act(.)) %>%
  arrange(steroids_rx, steroids_opt_poss, steroids_opt_act)

std_border <- fp_border(color = "gray")

ft <- flextable(df_tt) %>%
  set_header_labels(
    steroids_rx = 'Antenatal steroids given',
    steroids_opt_poss = 'Optimal Adminstration Possible',
    steroids_opt_act = 'Optimal Adminstration Achieved',
    valid = 'Logic Validity') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header") %>% 
  bg(j = 4, bg = function(x){ifelse(x, 'forestgreen', 'red4')}) %>%
  color(j = 4, color = 'white')
ft
```

## Antenatal magnesium sulphate section

### Antenatal magnesium sulphate given field

```{r tt_mgso4_rx, echo = FALSE}
df_tt <- data.frame(
  expand.grid(
    gestation = c('<26+6', '27 - 27+6', '28 - 29+6', '30 - 31+6', '32 - 33+6', NA),
    mgso4_rx = c('No', 'Yes', NA)
  )) %>%
  mutate(valid = fnCheck_mgso4_rx(.)) %>%
  arrange(gestation, mgso4_rx)

std_border <- fp_border(color = "gray")

ft <- flextable(df_tt) %>%
  set_header_labels(
    gestation = 'Gestation Length',
    mgso4_rx = 'Antenatal MgSO4 given',
    valid = 'Logic Validity') %>%
  set_table_properties(layout = "autofit", width = .5) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header") %>% 
  bg(j = 3, bg = function(x){ifelse(x, 'forestgreen', 'red4')}) %>%
  color(j = 3, color = 'white')
ft
```
 
### Antenatal magnesium sulphate administration optimisation possible

```{r tt_mgso4_opt_poss, echo = FALSE}
df_tt <- data.frame(
  expand.grid(
    gestation = c('<26+6', '27 - 27+6', '28 - 29+6', '30 - 31+6', '32 - 33+6', NA),
    mgso4_rx = c('No', 'Yes', NA),
    mgso4_opt_poss = c('No', 'Yes', NA)
  )) %>%
  mutate(valid = fnCheck_mgso4_opt_poss(.)) %>%
  arrange(gestation, mgso4_rx, mgso4_opt_poss)

std_border <- fp_border(color = "gray")

ft <- flextable(df_tt) %>%
  set_header_labels(
    gestation = 'Gestation Length',
    mgso4_rx = 'Antenatal MgSO4 given',
    mgso4_opt_act = 'Optimal Adminstration Possible',
    valid = 'Logic Validity') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header") %>% 
  bg(j = 4, bg = function(x){ifelse(x, 'forestgreen', 'red4')}) %>%
  color(j = 4, color = 'white')
ft
```

### Antenatal magnesium sulphate administration optimisation achieved

```{r tt_mgso4_opt_act, echo = FALSE}
df_tt <- data.frame(
  expand.grid(
    gestation = c('<26+6', '27 - 27+6', '28 - 29+6', '30 - 31+6', '32 - 33+6', NA),
    mgso4_rx = c('No', 'Yes', NA),
    mgso4_opt_poss = c('No', 'Yes', NA),
    mgso4_opt_act = c('No', 'Yes', NA)
  )) %>%
  mutate(valid = fnCheck_mgso4_opt_act(.)) %>%
  arrange(gestation, mgso4_rx, mgso4_opt_act)

std_border <- fp_border(color = "gray")

ft <- flextable(df_tt) %>%
  set_header_labels(
    gestation = 'Gestation Length',
    mgso4_rx = 'Antenatal MgSO4 given',
    mgso4_opt_possible = 'Optimal Adminstration Possible',
    mgso4_opt_act = 'Optimal Adminstration Achieved',
    valid = 'Logic Validity') %>%
  set_table_properties(layout = "autofit", width = .9) %>%
  hline(part = "body", border = std_border) %>%
  vline(part = "all", border = std_border) %>%
  bold(bold = TRUE, part = "header") %>% 
  bg(j = 5, bg = function(x){ifelse(x, 'forestgreen', 'red4')}) %>%
  color(j = 5, color = 'white')
ft
```